---
title: "LandWeb_summary Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'LandWeb_summary', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
  bibliography: citations/references_LandWeb_summary.bib
citation-style: citations/ecology-letters.csl
link-citations: true
always_allow_html: true
---

# LandWeb_summary Module

<!-- the following are text references used in captions for LaTeX compatibility -->
(ref:LandWeb-summary) *LandWeb_summary*

```{r setup-LandWeb-summary, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## change to eval = TRUE if all chunks are to be evaluated

## get citation style
if (!file.exists("citations/ecology-letters.csl")) {
  dir.create("citations", showWarnings = FALSE)
  download.file("https://www.zotero.org/styles/ecology-letters", destfile = "citations/ecology-letters.csl")
}

if (!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

dir.create("figures", showWarnings = FALSE)

download.file(url = "https://img.shields.io/badge/Made%20with-Markdown-1f425f.png",
              destfile = "figures/markdownBadge.png",
              mode = 'wb')
```

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = "LandWeb_summary", path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

## Module Overview

### Module summary

LandWeb simulation post-processing and summary creation.

<!-- TODO: add more details from LandWeb development document -->

### Module inputs and parameters

Table \@ref(tab:moduleInputs-LandWeb-summary) shows the full list of module inputs.

```{r moduleInputs-LandWeb-summary, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_inputs <- SpaDES.core::moduleInputs("LandWeb_summary", "..")
knitr::kable(df_inputs,
             caption = "List of (ref:LandWeb-summary) input objects and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

Provide a summary of user-visible parameters (Table \@ref(tab:moduleParams-LandWeb-summary))


```{r moduleParams-LandWeb-summary, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_params <- SpaDES.core::moduleParams("LandWeb_summary", "..")
knitr::kable(df_params, caption = "List of (ref:LandWeb-summary) parameters and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

### Events

<!-- TODO: add more details based on module code + LandWeb develpment doc -->

### Plotting

<!-- TODO: add more details based on module code + LandWeb develpment doc -->

### Saving

<!-- TODO: add more details based on module code + LandWeb develpment doc -->

### Module outputs

#### Large Patches Data for study region

- Large Patches Data (`.csv`)
- Large patches histograms (`.png`)

#### Leading Vegetation Cover Data for study region

- Leading Vegetation Cover Data (`.csv`)
- Leading Vegetation Cover histograms (`.png`)
- Leading Vegetation Cover boxplots (`.png`)

Description of the module outputs (Table \@ref(tab:moduleOutputs-LandWeb-summary)).

```{r moduleOutputs-LandWeb-summary, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("LandWeb_summary", "..")
knitr::kable(df_outputs, caption = "List of (ref:LandWeb-summary) outputs and their description.") %>%
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

### Links to other modules

Initially developed for use with the [LandWeb](https://github.com/PredictiveEcology/LandWeb) model.

### Getting help

-   <https://github.com/PredictiveEcology/LandWeb_summary/issues>
